`r params$doc_title`

### 2023-04-18 scripts/MSc.Rmd
changed to GSD only, no GBC

plot_data1b <- df_cum_expl_var %>% 
  pivot_longer(cols = c(cum_expl_varX2, cum_expl_varU, cum_expl_varY)) %>% 
  mutate(name = factor(name, labels = c("% var(U)", "% var(X)", "% var(Y)")),
         name = factor(name, levels = c("% var(X)", "% var(Y)", "% var(U)") )
         )
## plot
ggplot(plot_data1b, aes(x=n, y=value, col=name))+
  geom_point(alpha=0.6)+
  geom_line(alpha=0.6)+
  geom_line(aes(x=n, y=count_IVs_scaled, col="Number of IVs"), linetype="dotdash")+
  scale_x_continuous(name = paste0("Size of sample ", as.roman(1)),  # 2-sample-MR or label "Study Size"
                     labels = comma, 
                     breaks = N_annotation, #c( 10000, n[7:length(n)]),
                     limits = c(10000, 300000))+
  #ylab("% variance explained by IVs")+
  labs(title = "Figure 1",
       col='', 
       caption = "Relationship between sample size, average number of instrumental variables (IVs) and variance of traits explained by the IVs"
       ) +
  scale_y_continuous(
    # Features of the first axis
    name = "% variance explained by IVs",
    # Add a second axis and specify its features
    sec.axis = sec_axis(~./scale_factor, name="Number of IVs"),
    limits = c(0,5)
  ) + 
  theme_few()+
  #scale_colour_few() +
  #scale_color_manual(name = "", values = c("% var(U)" = "red", 
  #                                         "% var(X)" = "blue", 
  #                                         "% var(Y)" = "darkblue", 
  #                                         "Number of IVs" = "black"
  #                                         ))
  #
  scale_color_manual(name = "", values = c("% var(U)" = ggthemes_data$few$colors$Dark[2,2][[1]], 
                                           "% var(X)" = ggthemes_data$few$colors$Dark[3,2][[1]], 
                                           "% var(Y)" = ggthemes_data$few$colors$Dark[4,2][[1]], 
                                           "Number of IVs" = "black"),
                     # order
                     breaks = c( "Number of IVs", "% var(X)", "% var(Y)", "% var(U)")
  ) -> fig01b.update
fig01b.update  # USE THIS

>>>>

plot_data1b <- df_cum_expl_var %>% 
  pivot_longer(cols = c(cum_expl_varX2, cum_expl_varU, 
                        #cum_expl_varY
                        )) %>% 
  mutate(name = factor(name, labels = c("% var(Y)", "% var(X)")) #, "% var(Y)")),   # change made on 2023-04-18
         #name = factor(name, levels = c("% var(X)", "% var(Y)", "% var(U)") )
         )
## plot
ggplot(plot_data1b, aes(x=n, y=value, col=name))+
  geom_point(alpha=0.6)+
  geom_line(alpha=0.6)+
  geom_line(aes(x=n, y=count_IVs_scaled, col="Number of IVs"), linetype="dotdash")+
  scale_x_continuous(name = paste0("Size of sample ", as.roman(1)),  # 2-sample-MR or label "Study Size"
                     labels = comma, 
                     breaks = N_annotation, #c( 10000, n[7:length(n)]),
                     limits = c(10000, 300000))+
  #ylab("% variance explained by IVs")+
  labs(title = "Figure 1",
       col='', 
       caption = "Relationship between sample size, average number of instrumental variables (IVs) and variance of traits explained by the IVs"
       ) +
  scale_y_continuous(
    # Features of the first axis
    name = "% variance explained by IVs",
    # Add a second axis and specify its features
    sec.axis = sec_axis(~./scale_factor, name="Number of IVs"),
    limits = c(0,5)
  ) + 
  theme_few()+
  #scale_colour_few() +
  #scale_color_manual(name = "", values = c("% var(U)" = "red", 
  #                                         "% var(X)" = "blue", 
  #                                         "% var(Y)" = "darkblue", 
  #                                         "Number of IVs" = "black"
  #                                         ))
  #
  scale_color_manual(name = "", values = c(#"% var(U)" = ggthemes_data$few$colors$Dark[2,2][[1]], 
                                           "% var(X)" = ggthemes_data$few$colors$Dark[3,2][[1]], 
                                           "% var(Y)" = ggthemes_data$few$colors$Dark[4,2][[1]], 
                                           "Number of IVs" = "black"),
                     # order
                     breaks = c( "Number of IVs", "% var(X)", "% var(Y)")  #, "% var(U)")
  ) -> fig01b.update
fig01b.update  # USE THIS
